### 2017-04-07 paper/evaluation.tex
pass on rq5

We investigated this six projects further, and one of them contained a
false-negative result from \numRQC{}, which means that a configuration file
is compacted inside a Java container. One of them considered a
distributed CI server as parallelism. Two of those projects had a
custom JUnit test runner, which handles the parallelism itself. The
last two projects run the parallelism inside the test method, one runs
a manually created Thread to run some tests, and the other runs in
parallel by using Java 8 collection streams, that allows the
developers to iterate over a list in parallel.

>>>>

We investigated this six projects further, and one of them contained a
false-negative result from \numRQC{}, which means that a \pomf{}
is compacted inside a \CodeIn{jar} file. One of them considered a
distributed CI server as parallelism. Two of those projects had a
custom JUnit test runner, which handles the parallelism itself. The
last two projects run the parallelism inside the test method, one runs
a manually created Thread to run some tests, and the other runs in
parallel by using Java 8 collection streams, that allows the
developers to iterate over a list in parallel.
